Constant Error Tolerance Computational Fuzzy Extractors

### 2014-01-29 constantRate/ConstCompFuzzExt.tex
Working on sampler stuff

\section{Reducing Alphabet Size}
\consref{cons:first construction} is a computational fuzzy extractor with $gap<0$.  Unfortunately, each block is individually obfuscated causing the blocks to be of super-polynomial size~(our analysis was in the case where the blocks where exponential in the security parameter).  In this section, we present a generalization of \consref{cons:first construction} where the values being obfuscated are sampled from the blocks of the source, but blocks are not individually obfuscated.  Unfortunately, obfuscated multiple blocks together decreases the effective error tolerance.  
\begin{construction}
\label{cons:sampling}
Let $n$ be a security parameter.
Let $Z$ be an alphabet where $|Z| = \Omega(n)$, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $Z$.  Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \epsilon_{code})$ code.  Let $\eta = \omega(\log n)$ be some function such that $\eta \log (Z) = \omega(\log n)$.  Let $\mathcal{O}$ be a $\ell$-composable obfuscator for the family of point functions over $\zo^\eta$.  Define $\gen, \rep$ as:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item Sample $c\leftarrow C$.
\item For $i=1,..., \ell$:
\begin{itemize}
\item Sample $j_{i, 1},..., j_{i, \eta}\overset{\$}\leftarrow \{1,..., \gamma\}$
\item If $c_i = 0$: 
\subitem Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
\subitem Set $\rho_i = \mathcal{O}(I_{w_i})$.
\subitem Set $p_i = \rho_i, j_{i, 1},..., j_{i, \eta}$.
\item If $c_i = 1$: Sample $r_i \leftarrow U_n$. 
\subitem Let $p_i = \mathcal{O}(I_{r_i}) j_{i,1},..., j_{i, \eta}$.
\end{itemize}
\item Output $(c, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ 
\item For $i=1,..., \ell$:
\begin{itemize}
\item Parse $p_i$ as $\rho_i, j_{i, 1},..., j_{i, \eta}$.
\item Set $v_i = w_{j_{i, 1}},..., w_{j_{i, \eta}}$.
\item If $\rho_i(w_i') = 1$ set $c_i' = 0$.
\item Else set $c_i' = 1$.
\end{itemize}
\item Set $c = \decode(c')$.
\item Output $c$.
\end{enumerate}
\vspace{0.37in}
\end{minipage} 
\end{tabular}
\end{center}
\end{construction}

The main change in \consref{cons:sampling} is that the obfuscated values are concatenated alphabet symbols of $W$.  In the setting where each symbol of $W$ is long enough for secure obfuscation, \consref{cons:sampling} is essentially the same as \consref{cons:first construction}.  As before we must show security and correctness of \consref{cons:sampling}.  For security, the main argument is that each of the $v_i$ created has enough entropy to be unguessable.  We show this in the setting of block fixing sources~\cite{KZ07}.  This argument comes from the sampling literature~(used to create locally computable randomness extractors~\cite{lu2002hyper,vadhan2003constructing}).  For correctness we must show that the probability for each symbol $v_i \neq v_i'$ is a small constant so that $c'$ will be corrected to $c$.

\subsection{Security of \consref{cons:sampling}}
In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $v_i$ has entropy on its own.  Consider a source with entropy $\lambda$.  Then the expected entropy of 
\begin{align*}
\expe[\Hoo(V_i)] &=\expe[\text{entropy of each uniform }w_j] (\text{number of }w_j\text{ selected})\\
&=\frac{\lambda}{\gamma} \times \eta= \frac{\lambda \eta}{\gamma}.
\end{align*}
This value is super-logarithmic when $\lambda = \omega (\frac{\gamma \log n}{\eta})$.

@@

\subsection{Correctness of \consref{cons:sampling}}
The argument that $1\rightarrow 0$ flips are extremely unlikely carries over from \consref{cons:first construction}.  In this section, we analyze what values of $t$ will yield a small constant likelihood of error between $v_i$ and $v_i'$ yielding a constant probability of bit flip $0\rightarrow 1$ between $c$ and $c'$.  Consider a single index $i$ and let $t$ be the number of errors between $w$ and $w'$.  Then 
\begin{align*}
\Pr[v_i = v_i' ] &= \Pr[w_{j_{i,1}} = w_{j_{i,1}}' \wedge ... \wedge w_{j_{i, \eta/|Z|}} = w_{j_{i, \eta}}']\\
&=\Pr[w_{j_{i,1}} = w_{j_{i,1}}'] \times ... \times \Pr[w_{j_{i, \eta/|Z|}} = w_{j_{i, \eta}}']\\
&=\left (1-\frac{t}{\gamma}\right)^{\eta}
\end{align*} 
This value is $\Theta(1)$ when $t = \Theta(\frac{\gamma }{\eta})$.
\bnote{finish}

\subsection{Discussion}
As shown above we get security when $\lambda = \omega(\gamma \log n/\eta)$ and correctness when $t = \Theta(\gamma /\eta)$.  This yields:
\begin{align*}
gap &= \Hoo(W) -\log |B_t| \\
&< \omega(\frac{\gamma  \log n}{\eta} ) - (\Theta(t \mu) + \log {\gamma \choose t})\\
&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \mu^2}{\eta}))\\
&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \log |Z|}{\eta}))\\
&= \omega(\frac{\gamma \log n}{\eta})
\end{align*}
%Taking $\gamma = \Omega(n)$ and $\eta = \log^c n$ yields a negative $gap$.
\bnote{finish}
\bibliographystyle{alpha}
\bibliography{crypto}

>>>>

\section{Sample-then-Obfuscate}
\consref{cons:first construction} is a computational fuzzy extractor with $gap<0$.  In this section, we present a generalization of where the values being obfuscated are sampled from the blocks of the source, but blocks are not individually obfuscated.  This has two advantages, first it simplifies the type of sources we consider as we no longer need high entropy blocks.  Second, it allows us to decrease the size of each block from exponential to a super polynomial $2^{\log^c n}$ for some $c>0$.  Unfortunately, obfuscating multiple blocks together decreases the effective error tolerance.  In ordering for sampling to work properly, we need a source that is likely contribute some entropy from a randomly chosen block.

\begin{definition}
\label{def:unordered source}
A distribution $W = W_1,..., W_\gamma$ is called a $(\alpha, \beta)$-unordered block source if there exists a set of indices $\mathcal{I}$ where $|\mathcal{I}| \geq \gamma - \beta$ such that the following holds:
\[
\forall i\in \mathcal{I}, \forall w_1,..., w_\gamma \in W_1,..., W_\gamma, \Hoo(W_i | W_1 = w_1,..., W_{i-1}=w_{i-1}, W_{i+1}=w_{i+1},..., W_\gamma = w_\gamma) \geq \alpha.
\]
\end{definition}

\defref{def:unordered source} is a generalization of block sources~(introduced by Chor and Goldreich~\cite{DBLP:journals/siamcomp/ChorG88}), an unordered block source is one where most blocks contribute some entropy conditioned on the value of the other blocks.  This is a strengthening of an unguessable block distribution~(\defref{def:block guessable}), however we will achieve security for significantly lower entropy levels than were necessary for block unguessable distributions.  
\begin{construction}
\label{cons:sampling}
Let $n$ be a security parameter.
Let $Z$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_i$ is over $Z$.  Let $t$ be the desired error tolerance and let $C\subset \zo^\ell$ be a $(\neigh_t, \epsilon_{code})$ code.  Let $\sample_\beta(\gamma)$ output a uniform subset of indices of $1,..., \gamma$ of size $\beta$. Let $\eta = \omega(\log n)$ be some function such that $\eta \log (Z) = \omega(\log n)$.  Let $\mathcal{O}$ be a $\ell$-composable f for the family of point functions over $\zo^\eta$.  Define $\gen, \rep$ as:

\begin{center}
\begin{tabular}{c|c}
\begin{minipage}{3in}
\textbf{\gen}
\begin{enumerate}
\item \underline{Input}: $w = w_1,..., w_\gamma$
\item Sample $c\leftarrow C$.
\item For $i=1,..., \ell$:
\begin{itemize}
\item Sample $j_{i, 1},..., j_{i, \eta}\leftarrow \sample_\eta(\gamma)$
\item If $c_i = 0$: 
\subitem Set $v_i = w_{j_{i,1}},..., w_{j_{i, \eta}}$.
\subitem Set $\rho_i = \mathcal{O}(I_{w_i})$.
\subitem Set $p_i = \rho_i, j_{i, 1},..., j_{i, \eta}$.
\item If $c_i = 1$: Sample $r_i \leftarrow U_n$. 
\subitem Let $p_i = \mathcal{O}(I_{r_i}) j_{i,1},..., j_{i, \eta}$.
\end{itemize}
\item Output $(c, p)$.
\end{enumerate}
 \end{minipage} &
\begin{minipage}{3in}
\textbf{\rep}
\begin{enumerate}
\item \underline{Input}: $(w', p)$ 
\item For $i=1,..., \ell$:
\begin{itemize}
\item Parse $p_i$ as $\rho_i, j_{i, 1},..., j_{i, \eta}$.
\item Set $v_i = w_{j_{i, 1}},..., w_{j_{i, \eta}}$.
\item If $\rho_i(w_i') = 1$ set $c_i' = 0$.
\item Else set $c_i' = 1$.
\end{itemize}
\item Set $c = \decode(c')$.
\item Output $c$.
\end{enumerate}
\vspace{0.37in}
\end{minipage} 
\end{tabular}
\end{center}
\end{construction}

The main change in \consref{cons:sampling} is that the obfuscated values are concatenated alphabet symbols of $W$.  This paradigm is similar to \emph{sample-then-extract} from the locally computable extractors literature~\cite{lu2002hyper,vadhan2003constructing}.  For this reason we call \consref{cons:sampling} \emph{sample-then-obfuscate}.  There is a crucial difference, our use of a computationally-secure primitive allows us to sample multiple times and only argue that each $v_i$ has sufficient has individual entropy.  In the information-theoretic setting, it would be necessary to argue about the joint entropy of the obfuscated values.  Our construction uses the na\"{i}ve sampler that takes truly random samples, the analysis is essentially the same for more sophisticated samplers that use fewer random bits.  Goldreich provides an accessible introduction to samplers~\cite{goldreich1997sample}.

As before we must show security and correctness of \consref{cons:sampling}.  For security, the main argument is that each of the $v_i$ has enough entropy to be unguessable.  For correctness we must show that the induced error rate in $v$ and $v'$ is a small constant so that $c'$ will be corrected to $c$ with overwhelming probability.

\subsection{Security of \consref{cons:sampling}}
In order to show security \consref{cons:sampling}, we show that with overwhelming probability each of the selected $v_i$ has entropy on its own.  This means that  $V_1,..., V_\ell$ is a block-unguessable distribution and security follows by \thref{thm:security of cons}.  Consider a source with entropy $\lambda$.  The expected number of selected blocks that have entropy at least $\alpha$ is $\frac{\gamma-\beta}{\gamma} \times \beta$.  A good sampler selects a within a constant fraction of the expected number of these blocks.

\begin{lemma}
\bnote{write a lemma about this}
\end{lemma}
%\begin{align*}
%\expe[\Hoo(V_i)] &=\expe[\text{entropy of each uniform }w_j] (\text{number of }w_j\text{ selected})\\
%&=\frac{\lambda}{\gamma} \times \eta= \frac{\lambda \eta}{\gamma}.
%\end{align*}
%This value is super-logarithmic when $\lambda = \omega (\frac{\gamma \log n}{\eta})$.  Note this is independent of how the entropy is distributed between blocks.  In particular, we make no assumptions about particular blocks being unguessable, only about the overall entropy rate.  This is a much more natural condition for a source than \defref{def:block guessable}.  
%To show security we need the entropy of all $v_i$ to be $\omega(\log n)$ with overwhelming probability.  This follows by an argument from the locally computable extractor literature.

\begin{theorem}
\label{th:samp sec}
Let $n$ be a security parameter and let $Z$ be some super-polynomially size alphabet.  Let $W = W_1,..., W_\gamma$ be a distribution where each $W_i$ is over $Z$.  Let 
\[
\Hoo(W) = \omega\left(\frac{\gamma \log n}{\eta}\right),
\] 
then for all $i$ and for all values of $j_{1,1},..., j_{\ell, \eta}$ the distribution $\delta(V_i | j_{1,1},..., j_{\ell, \eta} , V'_i ) <\epsilon_{sam}$ where $\Hoo(V_i') = \omega(\log n)$.\bnote{I think $\epsilon_{sam}$ will be a negligible for resultant entropy of $O(\beta \times \alpha \times (\mathcal{I}-\beta)/\mathcal{I})$.}
\end{theorem}

\begin{corollary}
\label{cor:samp unguess}
Let $n, Z, W$ be as in \thref{th:samp sec}, then for all $j_{1,1},..., j_{\ell, \eta}$, $V | j_{1,1},..., j_{\ell,\eta}$ is $\epsilon_{sam}$ close to a $(\poly(n), \alpha = \omega(\log n), 0)$-block unguessable distribution.  In particular, If $\mathcal{O}$ is an $\ell$-composable virtual black obfuscator with auxiliary inputs for point programs over $\zo^{\beta}$ that is $(s_{obf}, \epsilon_{obf})$-hard, then $H^{\hill}_{\epsilon', s_{obf}}(C | P) \geq |C|$ for $\epsilon' = 2\epsilon_{obf} + \ell(\epsilon_{sam} + 2^{-(\alpha-1)})$.
\end{corollary}
\begin{proof}
Direct result of \thref{th:samp sec}, \bnote{need a claim saying if all $W_i$ have entropy, we are block unguessable}, and \thref{thm:security of cons}.
\end{proof}

@@

\subsection{Correctness of \consref{cons:sampling}}
The argument that $1\rightarrow 0$ flips are extremely unlikely carries over from \consref{cons:first construction}.  In this section, we analyze what values of $t$ will yield a small constant likelihood of error between $v_i$ and $v_i'$ yielding a constant probability of bit flip $0\rightarrow 1$ between $c$ and $c'$.  Consider a single index $i$ and let $t$ be the number of errors between $w$ and $w'$.  Then 
\begin{align*}
\Pr[v_i = v_i' ] &= \Pr[w_{j_{i,1}} = w_{j_{i,1}}' \wedge ... \wedge w_{j_{i, \eta/|Z|}} = w_{j_{i, \eta}}']\\
&=\Pr[w_{j_{i,1}} = w_{j_{i,1}}'] \times ... \times \Pr[w_{j_{i, \eta/|Z|}} = w_{j_{i, \eta}}']\\
&=\left (1-\frac{t}{\gamma}\right)^{\eta}
\end{align*} 
This value is $\Theta(1)$ when $t = \Theta(\frac{\gamma }{\eta})$.
\bnote{finish, Chernoff, not far from expectation.}

\subsection{Discussion}
\bnote{need to write this once we have parameters in the two sections above.}
%As shown above we get security when $\lambda = \omega(\gamma \log n/\eta)$ and correctness when $t = \Theta(\gamma /\eta)$.  This yields:
%\begin{align*}
%gap &= \Hoo(W) -\log |B_t| \\
%&< \omega(\frac{\gamma  \log n}{\eta} ) - (\Theta(t \mu) + \log {\gamma \choose t})\\
%&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \mu^2}{\eta}))\\
%&= \omega(\frac{\gamma \log n}{\eta}) - (\Theta(\frac{\gamma \log |Z|}{\eta}))\\
%&= \omega(\frac{\gamma \log n}{\eta})
%\end{align*}
%%Taking $\gamma = \Omega(n)$ and $\eta = \log^c n$ yields a negative $gap$.
%\bnote{finish}
\bibliographystyle{alpha}
\bibliography{crypto}
